Accelerated evolution of convective simulations

### 2018-06-14 referee_process/first_submission/referee_response.tex

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[aps, 11pt, singlecolumn]{revtex4-1} % Set the font size (10pt, 11pt and 12pt) and paper size (letterpaper, a4paper, etc)
\usepackage{natbib}
\bibliographystyle{apsrev}
\usepackage{setspace}

\begin{document}
\newenvironment{myquotation}{
\begin{quotation}
\itshape
}{ 
\end{quotation}
}
%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------
\noindent
Dear Eckart, other PRFluids editors, and anonymous referees,
$\,$\newline

\begin{singlespace}
We return our revised manuscript, ``Accelerated evolution in
convective simulations,'' addressing the concerns of the referee reports.
We would like to point out a few major changes in this version of the manuscript.
A new section, ``Computational time-savings of AE'' has been added after the
results section and before the conclusion section. In this section, we directly
compare the computational cost of AE and SE for select simulations and we discuss
the computational benefits of AE.  Furthermore, the final section of our paper
is now titled ``Discussion \& Conclusions;'' we have removed a vast amount
of speculation regarding extensions of AE from this section and have added
a paragraph containing some caveats regarding challenges that users will face in
extending AE to more difficult systems.  In addition to these changes in the text,
we have added a new Fig. 2 which compares the evolution of Nu and the
mean temperature in AE and SE, and we have added some accompanying text for this
figure to the results section.  Small changes in the text throughout the paper have
been made for clarity where these changes were requested by the reports.

@@

\newpage
\noindent
\Large{\textbf{Response to first referee:}}\newline$\,$\newline\indent

\begin{myquotation}
This paper describes a technique for accelerating the convergence to
thermal equilibrium in convective DNS simulations where such
convergence from an initial conductive state would be long. The
technique is essentially to evolve a DNS for for a while, collect the
background state non-equilibrium fluxes, and then solve a mean field
boundary value problem with scaled version of these fluxes for a new
background state in thermal equilibrium, then use this to restart the
DNS. These, or very similar techniques, have been used by many in the
past, although to my knowledge, as the authors here also claim, they
have not been explicitly written down in a paper. The authors have
gone to the trouble of doing this, not only providing a fairly
detailed prescription of the technique, but also some evidence of its
usefulness, albeit in a very simple case where it will definitely work
which is perhaps not totally representative. I guess I think this
paper is overall worthwhile, since it provides a place for newcomers
to the business to find some potentially time-saving help, even though
the ideas are not original. I think the most important issue with this
paper is that its claims of more universal applicability are somewhat
naive. I would suggest they temper these assertions substantially.

Basic questions:

How confident can one be that the BVP puts you closer to a nonlinear
saturated state than where you were? For example, in highly nonlinear
(turbulent) problems, there may be multiple states, maybe even
multiple stable states, with different background properties. Is it
possible to guarantee that you are not putting the system into an
equilibrium but unstable state, from which an equally long evolution
to a stable state is required? For the simple problems shown here,
this is perhaps not likely, but for very high degrees of turbulence,
or situations where unknown instabilities may exist, this process may
not be so successful perhaps? This is again a factor in my hesitation
about the total applicability of this technique across many problems
beyond the one the authors present.
\end{myquotation}
All of the statistical tests that we have performed in this work point towards
the evolved AE solution and SE solution being consistent.
It is true that there may be multiple stable states, and there
is no guarantee that the BVP puts the solution into the same stable state as
SE. We have included this caveat in our final discussion section.

@@

\begin{myquotation}
IV:

I don’t understand ``$10^{3+2/3}$''? Why is written like this?
\end{myquotation}
To determine the Ra of our simulations, we take even sized steps in log space
(3 per decade). We have changed 3 + 2/3 to 3.67 for easier reading.

\begin{myquotation}
I am not convinced that the whole ``2D and 3D scaling laws'' section
adds anything at all to this paper. It shows that this technique can
be used but so does the single example that is interrupted by this
piece. It is somewhat interesting for the scaling laws found
themselves, but it sounds like this should be in a different paper
because there is not enough explanation to understand things totally
here. I feel like the examples before and after this section are
sufficient to make the point about the AE scheme.
\end{myquotation}
We feel that it is important to show that AE works across some swath of parameter
space, in order to demonstrate its robustness for the problem presented here.
We have trimmed the text of the scaling laws section and reduced speculation in
order to keep the paper on topic. We have also replaced Re with Pe in this
section in order to reinforce the point that we are interested in high Pe
convection (since Pr = 1, Re = Pe numerically, so only labels have changed).

\begin{myquotation}
When discussing the PDFs, the author refer to the ``modes" of the PDF?
This sounds a bit odd to me. Do they mean the peaks? The phrase
``temperature fluctuations off of the modes'' is particularly baffling!
\end{myquotation}
We have replaced ``modes'' with ``maxima.''

\begin{myquotation}
The fact that the mean temperature profile is off by a constant factor
almost everywhere is a bit disturbing, even if the factor is small.
Does continued iteration of AE not get rid of this? If not, then this
is significant, because it would take a thermal relaxation time again
to correct this issue.
\end{myquotation}
We have added a paragraph to the ``accelerated evolution recipe'' appendix.
In it, we discuss the fact that AE can be iteratively solved until you converge
to a desired criterion, and that we were only aiming for O(1\%) in this
paper. With a smaller convergence criterion, the user
could get closer to the evolved SE solution, decreasing the separation
between the temperature PDFs seen in what is now Fig. 5. 
However, smaller convergence criteria
come with significant computational cost (the horizontal averages must be
better converged, and likely more iterative solves must be performed).

@@

The example performed was the most likely to succeed. The 2D cases
were essentially rolls. Were the 3D cases still essentially 2D rolls
too (since the scalings came out the same)? What about larger aspect
ratio and more turbulence cases where the dynamics would be more
complex? Keeping things smooth certainly enhances the likelihood of a
simple scaling of the nonlinear fluxes working.

I think the projections for more complicated problems mentioned are
naive. If there is any nonlinear adjustment to the convective region,
e.g. penetrative convection, then the technique is far less likely to
be simply successful in the current form. The assumption of fully
convective and thermal boundary layers remaining in place is a big
one, and this is not really acknowledged. The authors do mention
penetrative convection and do indeed say that only a stiff case would
work under these premises, but this is a bit hidden, I think, and
needs to be emphasized more. For example, the penetrative ice-water
problem even in Boussinesq would not work well with this technique I
think, since the penetrative region can deepen dramatically, and
adjust the radiative flux to match the substantially changed
convective flux.

Furthermore, the compressible case is much more danger prone than
envisioned here. I suspect that in the iteration to accelerate, any
mismatch in the fluctuations and the estimated means in the DNS will
lead to major transients in the form of sound waves, which can totally
destroy a compressible evolution by reducing the tilmestep
substantially, so this technique may have drawbacks if there is not
filtering of sound waves somehow. The authors have glossed over these
problems in their eagerness to extol the virtues of their scheme.

I think the claims of this method working in many more situations need
to be examined more thoroughly before being made so boldly here.
\end{myquotation}
%contained too much speculation.
We agree that our intial conclusion section was over-eager. We have 
greatly reduced the amount of text spent on speculation surrounding
extensions of the AE method, and have added a paragraph warning the
reader that not all extensions will be as simple (or guaranteed to work)
as the case studied here.

\newpage
\noindent
\Large{\textbf{Response to second referee:}}\newline$\,$\newline\indent
\begin{myquotation}
$\,$\\\vspace{-1.25cm}
\begin{enumerate}
\item The authors should provide clarification on what the following terms mean: ``thermal equilibration'', ``thermally relaxed'', and ``thermal convergence''. Also, are these terms related to statistically steady state?
\end{enumerate}
\end{myquotation}
All three of these phrases are equivalent, and we have replaced all mentions of
thermal equilibration, relaxation, and thermal convergence with ``thermal
equilibration'' or ``thermally equilibrated'' throughout the paper. This term
is explained in pargraph 2 of the introduction.
\begin{myquotation}
$\,$\\\vspace{-1.25cm}
\begin{enumerate}
\setcounter{enumi}{1}
\item What is the ``Kelvin-Helmholtz timescale''?
\end{enumerate}
\end{myquotation}
The Kelvin-Helmholtz timescale is 
$$
t_{\text{KH}} = \frac{E}{L},
$$
where $E$ is the thermal energy in a system, and $L$ is the luminosity
(energy output / time). It is an estimate of the timescale
of thermal evolution of a system 
(e.g., a star). Since the point we were trying to make is that ``the mean 
thermodynamic structure of the Sun evolves \emph{really} slowly,''
we have removed this jargon and said this more clearly in paragraph 3 of the intro.

\begin{myquotation}
$\,$\\\vspace{-1.25cm}
\begin{enumerate}
\setcounter{enumi}{2}
\item The authors note that the bootstrapping method is susceptible to hysteresis effects. They should provide examples of where such effects have been observed.
\end{enumerate}
\end{myquotation}
We misspoke. We have not specifically seen hysteresis effects (nor have we seen
this in the literature).  We meant to say that in simulations where there are
multiple solution branches (e.g., a convective roll and a shearing solution),
bootstrapping a solution on one branch to different parameters with the same
solution branches tends to result in a solution on the 
same solution branch.

@@

We have corrected our error and made our meaning clearer.

\begin{myquotation}
$\,$\\\vspace{-1.25cm}
\begin{enumerate}
\setcounter{enumi}{3}
\item It is true that direct numerical simulation of turbulent thermal convection is expensive. However, the highest Ra simulation run by Stevens et al. reaches a stationary state in a few hundreds of free-fall times. Hence, what is the necessity of running simulations for ``thousands or millions of free-fall times''?
\end{enumerate}
\end{myquotation}
We have added a new Fig. 2 to address this question. In general, we find that
the heat transport reaches its final, time-stationary mean
value very quickly (see panels (a) and (b) of Fig. 2). However, the thermal 
structure, kinetic energy, and fluctuations of heat transport away from the mean
can still slowly evolve for long timescales
despite the flows being relatively statistically stationary. The purpose of
running for many, many free-fall times is to converge the thermal profile of
the domain to ensure that the full system is in a steady state.

@@

\begin{myquotation}
$\,$\\\vspace{-1.25cm}
\begin{enumerate}
\setcounter{enumi}{6}
\item Could the authors construct plots of Nu vs. t (like in figure 2) for both AE and SE starting from t = 0? I would like to understand how Nu(t) evolves with time in the AE cases.
\end{enumerate}
\end{myquotation}
We have created this plot as part of a reponse to point 4. Please refer to the
new Fig. 2 in the text.

\begin{myquotation}
$\,$\\\vspace{-1.25cm}
\begin{enumerate}
\setcounter{enumi}{7}
\item I diasgree with the authors’ statement that “Previous studies in 2D convection may have avoided these time-varying Nu states by using bootstrapping techniques...” If one were to measure Nu(t) in the interior, then the sign of Nu would fluctuate between positive and negative. However, the time average would be always be positive. (This I know from my own work.)
\end{enumerate}
\end{myquotation}
The purpose of the previous Fig. 2 (now Fig. 3) was merely to show why we have
such large error bars on Nu in our Nu v. Ra plot (Fig. 4). Our aim is to show
the nature of the flow morphologies at times of high and low heat transport;
the instantaneous sign of Nu (positive or negative) is not what we are trying
to point out.

We have clarified the discussion in this portion of the paper.

\begin{myquotation}
$\,$\\\vspace{-1.25cm}
\begin{enumerate}
\setcounter{enumi}{8}
\item Have the authors studied convection with fixed temperature and no-slip conditions at the top and bottom surfaces? Have they compared the AE and SE results for that case?
\end{enumerate}
\end{myquotation}
We have not. We've used no-slip at both surfaces, 
but only mixed thermal boundary conditions. 
We don't forsee major difficulties in AE being applied to fixed T boundary 
conditions, and have added a brief discussion in section III challenges that
fixed flux or fixed temperature boundary conditions pose.

### 2018-06-14 tex/bvp_paper.tex
some updates to paper draft

\begin{table}
\caption{Shown are details regarding the computational cost of select
AE and SE runs in 2D and 3D. The supercriticality
($S$), coefficient resolution (nz, nx, ny), number of CPUs used
to perform the calculation ($N_{\text{CPU}}$), number of CPU-hours
used to perform the run ($t_{\text{CPU,AE/SE}}$), and ratio of CPU-hours
used in the AE run compared to the SE run are provided.
}
\label{table:speed}
\begin{center}
\begin{tabularx}{\textwidth}{ X X X X X X }
\hline																	
$S$	&	nz, nx$\times$ny	&	$N_{\text{CPU}}$	&	
$t_{\text{CPU,AE}}$ & $t_{\text{CPU, SE}}$ &$t_{\text{CPU,AE}}/t_{\text{CPU,SE}}$\\
\hline \hline \multicolumn{6}{c}{\vspace{-0.2cm}}\\
\multicolumn{6}{c}{\vspace{0.1cm}2D Runs} \\
\hline
$10^2$	&	64,	128	&	32    & 4.369 &  2.152    & 2.03  \\
$10^3$	&	128,256	&	64    & 20.63 &  53.25    & 0.387 \\
$10^4$	&	256,512	&	128   & 180.82&  1205.25  & 0.15  \\
$10^5$	&	512,1024&	256   & 2757.73& 24061.75 & 0.115 \\
\hline \hline \multicolumn{6}{c}{\vspace{-0.2cm}}\\
\multicolumn{6}{c}{\vspace{0.1cm}3D Runs} \\
\hline
$10^1$	&	32,	64$\times$64	& 512    &   106.15      &   61.5    & 1.73\\
$10^2$	&	64,	128$\times$128	& 512    &   111.92      &   185.35  & 0.6 \\
$10^3$	&	128,256$\times$256	& 2048   &   1426.39     &   6985.18 & 0.2 \\
$10^4$	&	256,512$\times$512	& 8192   &   23063.77    &   331,717 & 0.07\\
\hline																	
\end{tabularx}
\end{center}
\end{table}

The primary reason to use AE, rather than evolving all solutions through SE,
is because of the computational timesaving of such an approach. In table 
\ref{table:speed}, we compare cpu-hour cost for select
2D and 3D runs in which AE and SE solutions were compared. Times reported
for AE and SE runs do not include the time over which measurements were taken
in the equilibrated state, but rather represent the time required to reach a
fully equilibrated state under the AE or SE formalism. All simulations
were performed on Broadwell nodes on NASA's Pleiades supercomputer 
(Intel Xeon E5-2680v4 processors). The key metric which highlights the usefulness
of AE is the number of cpu-hours used for the AE run in units of cpu-hours used
for the SE run ($t_{\text{CPU,AE}}/t_{\text{CPU,SE}}$). We see that at low
resolution and low supercriticality, $t_{\text{CPU,AE}}/t_{\text{CPU,SE}} > 1$,
and AE is not useful. However, as $S$ grows, $t_{\text{CPU,AE}}/t_{\text{CPU,SE}}$
shrinks. At the highest supercriticalities for which AE and SE were compared
in this work, AE runs cost roughly an order of magnitude less computing time 
than SE runs.
 The additional computational expense of 3D runs compared
to 2D runs implies that 3D studies can greatly benefit from the proper implementation of AE.

While storing information about the mean state for the AE solve marginally
decreases the rate at which our solver timesteps, the first application of AE in a given
simulation (Fig.~\ref{fig:time_trace}c, at the arrow labeled ``1'') drastically
increases the average timestep by immediately progressing the simulation into
a more converged state. For the $S = 10^5$ case we examined in detail, the
average time step grew by a factor of 2-3 due to the decreased convective
velocities from the transient state to the evolved state. 
At $S = 10^7$, the AE solve immediately improved the timestep size 
by nearly a factor of 4.

@@

Here we studied the simplest possible case for the application of AE:
\RB convection at low aspect ratio with mixed thermal boundary. 
We anticipate that
this technique will be powerful in its extensions to more complicated studies.
To achieve AE in more complicated systems, one need only derive 
the steady-state, horizontally-averaged equations governing
the convective dynamics
(e.g., the analogs to Eqns.~(\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy}))
and couple those equations with knowledge of the boundary conditions
and current dynamics as described in
section \ref{sec:ae} and appendix \ref{appendix:recipe}.
In general, AE should be useful in studies where there are two disparate
timescales which must both be resolved and which cannot be overcome through
clever timestepping techniques.  Some avenues in which extensions of AE could
be beneficial for expanding the available parameter space of exploration
include studies of internally heated convection \cite{goluskin2016},
convection with height-dependent conductivities \cite{kapyla&all2017},
penetrative convection \cite{hurlburt&all1986,brandenburg&all2005,couston&all2017},
or fully compressible, stratified convection \cite{anders&brown2017}.
As AE is fundamentally a horizontally uniform adjustment to the thermodynamic
structure of the convective domain, it is unlikely that these techniques
should be applied straightforwardly to nonperiodic convective domains.

We conclude by noting that AE should be extended to these more complicated
studies with care. 
While AE was extremely effective in this simple case studied here
(where the aspect ratio was low, 
the bounds of the convective domain were pre-defined,
and the solutions were simple rolls),
this may not be the case for more complicated systems. For example, at
higher aspect ratios, multiple stable solution branches of various numbers of
convective rolls may exist, and there is no guarantee that AE and SE will
arrive at the same solution. 
Some assumptions which inform the AE solution, such as the assumption
that the convection
intially occupies the same space as the evolved convection, may not hold in
studies of penetrative convection, despite the fact that similar methods have
long been used in those studies \cite{hurlburt&all1986}.
Our work here should serve as a basis for determining if AE techniques are
valid and effective in more complex studies of convection.

@@

\appendix
\section{Table of Runs}
\label{appendix:run_table}
In Table \ref{table:run_parameters} we list key properties of all simulations
conducted in this work.  
\begin{table}
\caption{Simulation parameters. We report the supercriticality ($S$), Rayleigh number (Ra), 
and coefficient resolution (nz, nx, and ny are the number of coefficients in the
z, x, and y directions respectively).
Simulation run times required to reach convergence
are reported for the SE solutions ($t_{\text{therm}}$) and the AE solutions ($t_{\text{AE}}$).
The amount of time over which simulations measurements were taken in the evolved
state is listed ($t_{\text{avg}}$). All times are in freefall time units.  
The volume-averaged Nusselt number (Nu) of the
AE and SE solutions are shown.
In the upper part of the table, information pertaining to 2D runs is reported,
while information pertaining to 3D runs is in the lower part of the table.
}
\label{table:run_parameters}
\begin{center}
\begin{tabularx}{\textwidth}{ X X X X | X X X | X X }
\hline																	
$S$	&	Ra	&	nz	&	nx, ny	&	$t_{\text{therm}}$	&	$t_{\text{AE}}$	&	$t_{\text{avg}}$	&	Nu$_{\text{SE}}$	&	Nu$_{\text{AE}}$	\\
\hline \hline \multicolumn{9}{c}{\vspace{-0.2cm}}\\
\multicolumn{9}{c}{\vspace{0.1cm}2D Runs} \\
\hline
$10^{1/3}$	&	$2.79 \cdot 10^3$	&	32	&	64	&	$52.8$	&	$340$	&	100	&	1.46	&	1.46	\\
$10^{2/3}$	&	$6.01 \cdot 10^3$	&	32	&	64	&	$77.6$	&	$282$	&	100	&	1.95	&	1.95	\\
$10^1$	&	$1.30 \cdot 10^4$	&	32	&	64	&	$114$	&	$265$	&	100	&	2.43	&	2.42	\\
$10^{1 + 1/3}$	&	$2.79 \cdot 10^4$	&	32	&	64	&	$167$	&	$251$	&	100	&	2.54	&	2.54	\\
$10^{1 + 2/3}$	&	$6.01 \cdot 10^4$	&	32	&	64	&	$245$	&	$245$	&	100	&	3.14	&	3.14	\\
$10^2$	&	$1.30 \cdot 10^5$	&	64	&	128	&	$360$	&	$326$	&	100	&	3.8	&	3.8	\\
$10^{2 + 1/3}$	&	$2.79 \cdot 10^5$	&	64	&	128	&	$528$	&	$248$	&	100	&	4.71	&	4.71	\\
$10^{2 + 2/3}$	&	$6.01 \cdot 10^5$	&	64	&	128	&	$776$	&	$251$	&	100	&	5.5	&	5.5	\\
$10^3$	&	$1.30 \cdot 10^6$	&	128	&	256	&	$1.14 \cdot 10^3$	&	$268$	&	200	&	6.4	&	6.33	\\
$10^{3 + 1/3}$	&	$2.79 \cdot 10^6$	&	128	&	256	&	$1.67 \cdot 10^3$	&	$247$	&	500	&	6.87	&	6.95	\\
$10^{3 + 2/3}$	&	$6.01 \cdot 10^6$	&	256	&	512	&	$2.45 \cdot 10^3$	&	$275$	&	500	&	7.54	&	7.59	\\
$10^4$	&	$1.30 \cdot 10^7$	&	256	&	512	&	$3.60 \cdot 10^3$	&	$301$	&	500	&	8.83	&	8.83	\\
$10^{4 + 1/3}$	&	$2.79 \cdot 10^7$	&	256	&	512	&	$5.28 \cdot 10^3$	&	$317$	&	500	&	10.13	&	10.14	\\
$10^{4 + 2/3}$	&	$6.01 \cdot 10^7$	&	256	&	512	&	$7.76 \cdot 10^3$	&	$326$	&	500	&	11.65	&	11.69	\\
$10^5$	&	$1.30 \cdot 10^8$	&	512	&	1024	&	$1.14 \cdot 10^4$	&	$411$	&	500	&	14.02	&	14.18	\\
$10^{5 + 1/3}$	&	$2.79 \cdot 10^8$	&	512	&	1024	&	$1.67 \cdot 10^4$	&	$391$	&	500	&	---	&	16.21	\\
$10^{5 + 2/3}$	&	$6.01 \cdot 10^8$	&	512	&	1024	&	$2.45 \cdot 10^4$	&	$453$	&	500	&	---	&	18.58	\\
$10^6$	&	$1.30 \cdot 10^9$	&	1024	&	2048	&	$3.60 \cdot 10^4$	&	$436$	&	500	&	---	&	22.13	\\
$10^7$	&	$1.30 \cdot 10^{10}$	&	2048	&	4096	&	$1.14 \cdot 10^5$	&	$183$	&	170	&	---	&	38.29	\\
\\ \hline \hline \multicolumn{9}{c}{\vspace{-0.2cm}}\\
\multicolumn{9}{c}{\vspace{0.1cm}3D Runs} \\
\hline
$10^1$	&	$1.30 \cdot 10^4$	&	32	&	64$\times$64	&	$114$	&	$261$	&	100	&	2.42	&	2.42	\\
$10^2$	&	$1.30 \cdot 10^5$	&	64	&	128$\times$128	&	$360$	&	$249$	&	100	&	3.97	&	4	\\
$10^3$	&	$1.30 \cdot 10^6$	&	128	&	256$\times$256	&	$1.14 \cdot 10^3$	&	$243$	&	500	&	6.27	&	6.27	\\
$10^4$	&	$1.30 \cdot 10^7$	&	256	&	512$\times$512	&	$3.60 \cdot 10^3$	&	$244$	&	500	&	9.92	&	9.88	\\
\hline																	
\end{tabularx}
\end{center}
\end{table}

>>>>

\begin{table}
\caption{Shown are details regarding the computational cost of select
AE and SE runs in 2D and 3D. The supercriticality
($S$), coefficient resolution (nz, nx, ny), number of CPUs used
to perform the calculation ($N_{\text{CPU}}$), number of CPU-hours
used to perform the run ($t_{\text{CPU,AE/SE}}$), and ratio of CPU-hours
used in the AE run compared to the SE run are provided.
}
\setlength{\tabcolsep}{12pt}
\label{table:speed}
\begin{center}
\begin{tabularx}{0.72\textwidth}{ c r r c c c }
\hline																	
$S$	&	nz$\times$nx$\times$ny	&	$N_{\text{CPU}}$	&	
$t_{\text{CPU, SE}}$ & $t_{\text{CPU, AE}}$ &$t_{\text{CPU,AE}}/t_{\text{CPU,SE}}$\\
\hline \hline \multicolumn{6}{c}{\vspace{-0.2cm}}\\
\multicolumn{6}{c}{\vspace{0.1cm}2D Runs} \\
\hline
%2 sig figs, scientific notation, swap SE and AE, right justify Ncpu, 2 sig figs ratio, right justify communicates biggerness. 
$10^2$	&	64$\times$128	&	32    &  2.2              & 4.4               &     2.0  \\
$10^3$	&	128$\times$256	&	64    &  53               & 21                &     0.39 \\
$10^4$	&	256$\times$512	&	128   &  1.2$\times 10^3$ & 1.8$\times 10^2$  &     0.15  \\
$10^5$	&	512$\times$1024&	256   &  2.4$\times 10^4$ & 2.8$\times 10^3$  &     0.12 \\
\hline \hline \multicolumn{6}{c}{\vspace{-0.2cm}}\\
\multicolumn{6}{c}{\vspace{0.1cm}3D Runs} \\
\hline
$10^1$	&	32$\times$64$\times$64	    & 512       &   62                 &        1.1$\times 10^2$   & 1.7\\
$10^2$	&	64$\times$128$\times$128	& 512       &   1.9$\times 10^2$   &        1.1$\times 10^2$   & 0.60 \\
$10^3$	&	128$\times$256$\times$256	& 2048      &   7.0$\times 10^3$   &        1.4$\times 10^3$   & 0.20 \\
$10^4$	&	256$\times$512$\times$512	& 8192      &   3.3$\times 10^5$   &        2.3$\times 10^4$   & 0.070\\
\hline																	
\end{tabularx}
\end{center}
\end{table}

Computational timesaving is the primary reason to use AE rather than 
evolving all solutions through SE.
In table 
\ref{table:speed}, we compare cpu-hour cost for select
2D and 3D runs in which AE and SE solutions were compared. Times reported
for AE and SE runs only include the time required to reach an equilibrated
state, and do not include the time over which measurements were taken
in the equilibrated state (e.g., the green shaded regions of
Fig.~\ref{fig:time_trace}a\&c are not included in the $S = 10^5$ times).
All simulations
were performed on Broadwell nodes on NASA's Pleiades supercomputer 
(Intel Xeon E5-2680v4 processors). The key metric which highlights the usefulness
of AE is the number of cpu-hours used for the AE run in units of cpu-hours used
for the SE run ($t_{\text{CPU,AE}}/t_{\text{CPU,SE}}$). We see that at low
resolution and low supercriticality, $t_{\text{CPU,AE}}/t_{\text{CPU,SE}} > 1$,
and AE is not useful. However, as $S$ grows, $t_{\text{CPU,AE}}/t_{\text{CPU,SE}}$
shrinks. At the highest supercriticalities for which AE and SE were compared
in this work, AE runs cost roughly an order of magnitude less computing time 
than SE runs.
 The additional computational expense of 3D runs compared
to 2D runs implies that 3D studies can greatly benefit from AE.

Storing information about the mean state for the AE solve marginally
decreases the rate at which our solver timesteps. However, 
the first application of AE in a given simulation 
(e.g., Fig.~\ref{fig:time_trace}c, at the arrow labeled ``1'') drastically
increases the average timestep by fastforwarding the simulation into
a more stable state with lower convective velocities. 
For the $S = 10^5$ case we examined in detail, the
average time step grew by a factor of 2-3.
At $S = 10^7$, the AE solve immediately improved the timestep size 
by nearly a factor of 4.

@@

Here we studied the simplest possible case for the application of AE:
\RB convection at low aspect ratio with mixed thermal boundary conditions. 
We anticipate that
this technique will be powerful in its extensions to more complicated studies.
To achieve AE in more complicated systems, one need only derive 
the steady-state, horizontally-averaged equations governing
the convective dynamics
(e.g., the analogs to Eqns.~(\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy}))
and couple those equations with knowledge of the boundary conditions
and current dynamics as described in
section \ref{sec:ae} and appendix \ref{appendix:recipe}.
In general, AE should be useful in studies where there are two disparate
timescales which must both be resolved and which cannot be overcome through
clever timestepping techniques.  Some avenues in which extensions of AE could
be beneficial for expanding the available parameter space of exploration
include studies of internally heated convection \cite{goluskin2016},
convection with height-dependent conductivities \cite{kapyla&all2017},
penetrative convection \cite{hurlburt&all1986,brandenburg&all2005,couston&all2017},
or fully compressible, stratified convection \cite{anders&brown2017}.
As AE is fundamentally a horizontally uniform adjustment to the thermodynamic
structure of the convective domain, it is unlikely that these techniques
should be applied straightforwardly to nonperiodic convective domains.

We conclude by noting that AE should be extended to these more complicated
studies with care. 
While AE was extremely effective in this simple case studied here
(where the aspect ratio was low, 
the bounds of the convective domain were pre-defined,
and the solutions were simple rolls),
this may not be the case for more complicated systems. For example, at
higher aspect ratios, multiple stable solution branches 
may exist, and there is no guarantee that AE and SE will
arrive at the same solution. 
Some assumptions which inform the AE solution, such as the assumption
that the convection
intially occupies the same space as the evolved convection, may not hold in
studies of penetrative convection, despite the fact that similar methods have
long been used in those studies \cite{hurlburt&all1986}.
Our work here serves as a basis for determining if AE techniques are
effective in more complex studies of convection.

@@

\appendix
\section{Table of Runs}
\label{appendix:run_table}
In Table \ref{table:run_parameters} we list key properties of all simulations
conducted in this work.  
\begin{table}
\caption{Simulation parameters. We report the supercriticality ($S$), Rayleigh number (Ra), 
and coefficient resolution (nz, nx, and ny are the number of coefficients in the
z, x, and y directions respectively).
Simulation run times required to reach convergence
are reported for the SE solutions ($t_{\text{SE}}$) and the AE solutions ($t_{\text{AE}}$).
The amount of time over which simulations measurements were taken in the evolved
state is listed ($t_{\text{avg}}$). All times are in freefall time units.  
The volume-averaged Nusselt number (Nu) of the
AE and SE solutions are shown.
In the upper part of the table, information pertaining to 2D runs is reported,
while information pertaining to 3D runs is in the lower part of the table.
}
\label{table:run_parameters}
\begin{center}
\begin{tabularx}{\textwidth}{ X X r | X X X | X X }
\hline																	
$S$	&	Ra	&	nz$\times$nx$\times$ny$\,\,\,\,\,\,\,$	&	$t_{\text{SE}}$	&	$t_{\text{AE}}$	&	$t_{\text{avg}}$	&	Nu$_{\text{SE}}$	&	Nu$_{\text{AE}}$	\\
\hline \hline \multicolumn{8}{c}{\vspace{-0.2cm}}\\
\multicolumn{8}{c}{\vspace{0.1cm}2D Runs} \\
\hline
$10^{1/3}$	    &	$2.79 \cdot 10^3$       &	32$\times$64$\,\,\,\,\,\,\,$&	$52.8$	&	$340$	&	100	&	1.46	&	1.46	\\
$10^{2/3}$	    &	$6.01 \cdot 10^3$       &	32$\times$64$\,\,\,\,\,\,\,$&	$77.6$	&	$282$	&	100	&	1.95	&	1.95	\\
$10^1$	        &	$1.30 \cdot 10^4$       &  	32$\times$64$\,\,\,\,\,\,\,$&	$114$	&	$265$	&	100	&	2.43	&	2.42	\\
$10^{1 + 1/3}$	&	$2.79 \cdot 10^4$       &	32$\times$64$\,\,\,\,\,\,\,$&	$167$	&	$251$	&	100	&	2.54	&	2.54	\\
$10^{1 + 2/3}$	&	$6.01 \cdot 10^4$       &	32$\times$64$\,\,\,\,\,\,\,$&	$245$	&	$245$	&	100	&	3.14	&	3.14	\\
$10^2$	        &	$1.30 \cdot 10^5$       &	64$\times$128$\,\,\,\,\,\,\,$&	$360$	&	$326$	&	100	&	3.8	&	3.8	\\
$10^{2 + 1/3}$	&	$2.79 \cdot 10^5$       &	64$\times$128$\,\,\,\,\,\,\,$&	$528$	&	$248$	&	100	&	4.71	&	4.71	\\
$10^{2 + 2/3}$	&	$6.01 \cdot 10^5$       &	64$\times$128$\,\,\,\,\,\,\,$&	$776$	&	$251$	&	100	&	5.5	&	5.5	\\
$10^3$	        &	$1.30 \cdot 10^6$       &	128$\times$256$\,\,\,\,\,\,\,$&	$1.14 \cdot 10^3$	&	$268$	&	200	&	6.4	&	6.33	\\
$10^{3 + 1/3}$	&	$2.79 \cdot 10^6$       &	128$\times$256$\,\,\,\,\,\,\,$&	$1.67 \cdot 10^3$	&	$247$	&	500	&	6.87	&	6.95	\\
$10^{3 + 2/3}$	&	$6.01 \cdot 10^6$       &	256$\times$512$\,\,\,\,\,\,\,$&	$2.45 \cdot 10^3$	&	$275$	&	500	&	7.54	&	7.59	\\
$10^4$	        &	$1.30 \cdot 10^7$       &	256$\times$512$\,\,\,\,\,\,\,$&	$3.60 \cdot 10^3$	&	$301$	&	500	&	8.83	&	8.83	\\
$10^{4 + 1/3}$	&	$2.79 \cdot 10^7$       &	256$\times$512$\,\,\,\,\,\,\,$&	$5.28 \cdot 10^3$	&	$317$	&	500	&	10.13	&	10.14	\\
$10^{4 + 2/3}$	&	$6.01 \cdot 10^7$       &	256$\times$512$\,\,\,\,\,\,\,$&	$7.76 \cdot 10^3$	&	$326$	&	500	&	11.65	&	11.69	\\
$10^5$	        &	$1.30 \cdot 10^8$       &	512$\times$1024$\,\,\,\,\,\,\,$&	$1.14 \cdot 10^4$	&	$411$	&	500	&	14.02	&	14.18	\\
$10^{5 + 1/3}$	&	$2.79 \cdot 10^8$       &	512$\times$1024$\,\,\,\,\,\,\,$&	$1.67 \cdot 10^4$	&	$391$	&	500	&	---	&	16.21	\\
$10^{5 + 2/3}$	&	$6.01 \cdot 10^8$       &	512$\times$1024$\,\,\,\,\,\,\,$&	$2.45 \cdot 10^4$	&	$453$	&	500	&	---	&	18.58	\\
$10^6$	        &	$1.30 \cdot 10^9$       &	1024$\times$2048$\,\,\,\,\,\,\,$	&	$3.60 \cdot 10^4$	&	$436$	&	500	&	---	&	22.13	\\
$10^7$	        &	$1.30 \cdot 10^{10}$	&	2048$\times$4096$\,\,\,\,\,\,\,$	&	$1.14 \cdot 10^5$	&	$183$	&	170	&	---	&	38.29	\\
\\ \hline \hline \multicolumn{8}{c}{\vspace{-0.2cm}}\\
\multicolumn{8}{c}{\vspace{0.1cm}3D Runs} \\
\hline
$10^1$          &	$1.30 \cdot 10^4$	&	32$\times$64$\times$64$\,\,\,\,\,\,\,$   &	$114$	&	$261$	&	100	&	2.42	&	2.42	\\
$10^2$          &	$1.30 \cdot 10^5$	&	64$\times$128$\times$128$\,\,\,\,\,\,\,$   &	$360$	&	$249$	&	100	&	3.97	&	4	\\
$10^3$          &	$1.30 \cdot 10^6$	&	128$\times$256$\times$256$\,\,\,\,\,\,\,$	&	$1.14 \cdot 10^3$	&	$243$	&	500	&	6.27	&	6.27	\\
$10^4$          &	$1.30 \cdot 10^7$	&	256$\times$512$\times$512$\,\,\,\,\,\,\,$	&	$3.60 \cdot 10^3$	&	$244$	&	500	&	9.92	&	9.88	\\
\hline																	
\end{tabularx}
\end{center}
\end{table}
